Modelling potential environmental impacts of science activity in Antarctica

### 2024-12-12 paper/paper.qmd
frozen paper prior to mtg with Fraser

# get the sequence numbers of thes in the pts data
origin_is <- origin_pts |>
  st_nearest_feature(pts)

# make up a point dataset of these origins with randomly assigned importance
origin_vs <- pts |>
  mutate(id = row_number()) |>
  slice(origin_is) |>
  mutate(Importance = sample((seq(2, 50, 2) / 5) ^ 2, n(), 
                             replace = TRUE, prob = (seq(50, 2, -2) / 5) ^ 2))

@@

## Discussion and conclusions {#sec-discussion}

>>>>

# get the sequence numbers of thes in the pts data

origin_is <- origin_pts |>
  st_nearest_feature(pts)

# make up a point dataset of these origins with randomly assigned importance
origin_vs <- pts |>
  mutate(id = row_number()) |>
  slice(origin_is) |>
  # note: important here to avoid Importance values < 1!
  mutate(Importance = rgeom(n(), 0.1) + 1)

@@

## Discussion {#sec-discussion}
To cover:
+ Figure of the largest study site?
+ Limitations of the method:
  + Data concerns, esp. opportunistic nature of the GPS data
  + Would higher resolution network be useful?
  + Reliance of shortest paths as a guide to behaviour
  + Some minor issues regarding the difference between directed and undirected graphs
+ Relevance of radius limits on betweenness: the implicit model of movement in this approach (short horizons, no existing paths, 'keep going for half an hour in this general direction...')
+ Question of embedding paths, i.e., locking in more damage to some parts of the landscape vs others

## Conclusions {#sec-conclusions}
To cover:
+ Novelty of fitting land cover specific hiking functions
+ A method for exploring potential impacts in a novel environment
+ A method for proposing less damaging plans for expeditions
+ Other?
